---
title: ''
  html_document:
    df_print: paged
---

\newpage

# `r fontawesome::fa("binoculars")` Course overview.

In this section I describe and explain the course objectives, mechanics, and important information about academic integrity.

## Description.

<!-- EMF. `r fontawesome::fa("chart-line")` The course includes a COIL (Collaborative Online International Learning) activity with students at Universidad Pontificia Bolivariana in Colombia in the hope that students attain a degree of intercultural understanding. Econometrics is the branch of economics concerned with the use of mathematical and statistical methods describing economic systems. We define financial econometrics as the application of statistical techniques to answer problems in finance. For example, we might know from previous courses that there is a negative relationship between interest rates and stock prices, but we cannot know the size or the magnitude of this relationship unless we measure it and verify how strong or weak this relationship is by applying econometrics. Financial econometrics also allows us to incorporate data into existing financial models to empirically test their validity and find estimates which are significantly superior to informal *guesstimates*. Forecasting is also a common and popular task in financial econometrics. It is an integral part of the decision-making activities of management, as it can play an important role in many areas of a company. Most of this course is about forecasting methods that we commonly use in finance and economics. Forecasting is about predicting the future as accurately as possible, given all of the information available, including historical data and knowledge of any future events that might impact the forecasts. This subject can contribute to evolving from a student to a practitioner in the area of finance, especially because we are going to incorporate computational finance in R as a way to learn financial econometrics. The main electronic textbooks are the following: @49018680cf534023b6ae0f4e933c475d, and @lozanoEMF. Other good reference books based on R are @hanck2020introduction, @gujarati2012basic, @brooks2019introductory, @Oswaldeconometrics, @heiss2020usingR and @mcnulty2021handbook, @RundelIntroduction, @james2013introduction. For Python, see @heiss2020usingPython. Please see the course calendar at the end of this syllabus to review the topics, activities as well as the required readings. -->

ARF. `r fontawesome::fa("credit-card")` Financial risk management is about identifying, quantifying and managing financial risks. In this course we focus our attention on credit risk models and their corresponding computational applications in R. Credit risk refers to the probability of loss due to a borrower's failure to make payments on any type of debt. Credit risk management is the practice of mitigating losses by understanding how to measure the probability of default and the corresponding potential losses. Traditionally, courses like these rely only on firms as the main subject of study, but this course also incorporates issues related with individuals and countries which open an interesting avenue to apply financial and economic analysis. In fact, we can understand this course as a two-pillar course, one of them is about modern techniques and methodologies aimed to identify, quantify and manage financial risks, especially credit risk. The second pillar is about developing analysis skills and understanding the most relevant financial and economic challenges of Mexico. The main textbooks are the following: @Hull9 as it incorporates the most influential credit risk models in the financial industry, @crouhy2014essentials, @brealey2020principles as they present a comprehensive analysis of the various sources of risk in financial markets, and @lozanoARF which closes the gap between the model analysis and its corresponding computational modeling in R. A couple of complementary reference books are @hull2020machine, @james2013introduction. Please see the course calendar at the end of this syllabus to review the topics, activities as well as the required readings.

<!-- IF. `r fontawesome::fa("cogs")` Engineering is the branch of science and technology concerned with the design, building, use of engines, machines, and structures. In this sense, financial engineering is concerned with the design, modeling and use of combined financial techniques and instruments to build a strategy that changes or mitigates a given risk exposure. You will learn how to build a quantitative financial strategy, the nature of financial instruments like options, and understand the available tools and techniques we have to measure risk in finance as value at risk and GARCH models. The course is based on the legendary John C. Hull's textbook @Hull9 which is undoubtedly a very important reference in academia and the financial industry. This course represents a good foundation if you plan to study a master degree in Finance or if you want to pursue a professional certification in the area of quantitative finance. The second reference is @lozanoIF which closes the gap between the model analysis and its corresponding computational modeling in R. A good complementary reference book for this course is @goetzmann2014modern because it offers a very thorough and up-to-date presentation of modern portfolio analysis. Others are @brealey2020principles, @ruppert2011statistics and @james2013introduction, which seeks to balance the formal aspects of theory with the demands of practitioners. The beauty of financial engineering is that it allows us to incorporate knowledge from other related topics such as computational finance, financial derivatives and statistics to innovate and to come up with improved solutions to create valuable financial decisions. Please see the course calendar at the end of this syllabus to review the topics, activities as well as the required readings. -->

<!-- PMF. Traditional financial models expressed in assumptions, principles, functions and equations are fundamental tools to make better and more informed financial decisions. By incorporating the relevant technology, financial models can be expressed in computational code, which is the first step towards automation and allows us to expand the scope and limits of financial analysis. This course merges financial analysis, and financial modeling in order to translate models originally stated in paper into functional computational code. These kinds of skills are currently highly demanded and valued not only in the job market but also in research, FinTech and innovation projects. The main textbook is @lozanoPMF which has been developed to close the gap between the model analysis and its corresponding computational modeling in R. Some complementary reference books are @hull2020machine, @james2013introduction and @ruppert2011statistics. Please see the course calendar at the end of this syllabus to review the topics, activities as well as the required readings. -->

<!-- EFPI. \faSearchDollar \hspace{1 mm} Investment is normally referred to as a source of growth within a firm (and even a country). However, investment decisions can lead to negative outcomes depending on economic conditions or simply because of a poor risk assessment. In this course we will learn the basics and some of the advanced techniques available for evaluating investment projects. Examples of investment projects include financial products like investment funds or even firms. Investment projects usually require an initial payment now in exchange for future cash flows. Here, the problem arises when investment projects fail to generate those future cash flows. Evaluation of investment projects help us to understand how risky they are with respect to the promised future cash flows. The analysis and evaluation of investment projects allow us to understand how to make them more attractive, and discriminate between good and bad investment decisions. Our main textbook is @brealey2020principles. -->

<!-- MPA. Economics is the social science that allows us to comprehend the allocation of resources to satisfy needs. It is a social science because the allocation of resources is a human choice, thus it is based on human behavior rather than on natural laws such as in physics or chemistry. In this course we are going to learn microeconomics, which is the branch of economics that studies the economic behavior of single agents such as firms. Following the same logic, macroeconomics is the branch of economics that studies the aggregate behavior of many agents. Microeconomics helps us to better comprehend how individual agents – such as firms, consumers and governments – make informed and rational decisions in terms of assigning limited resources to unlimited wants and needs. This segmentation is convenient in order to elucidate the interactions between preferences, incentives, objectives and constraints within each particular economic agent. For example, an individual wants to consume goods and services to increase his or her well-being but at the same time the individual is restricted by a limited budget formed by income and wealth. Similarly, the firm is bound by regulatory issues, costs, scarce monetary resources, market conditions, asymmetric and imperfect information, but at the same time is looking forward to maximizing profits. Finally, any government would ideally be interested in providing public goods, decreasing poverty levels, promoting welfare and an appropriate competitive environment; although resources coming from taxes are limited and incentives are not always well aligned. Therefore, every single economic agent tries to do their best in order to allocate limited resources to satisfy unlimited needs and understanding microeconomics helps these economic agents to take better and more informed decisions as these decisions are based in a scientific approach rather than following an intuitive approach. Given that this process is perpetual and inherent in real-life, whoever that understands the foundations of microeconomic analysis, has a significant comparative advantage in business and management. This is why you are expected to understand microeconomics at an early stage in your undergraduate studies. -->


## Objectives.

The main objectives of the course is that you understand the course topics, learn to apply a variety of models in the area of financial economics and quantitative finance, and develop the required competences in the field. You will learn the topics by implementing the relevant quantitative techniques and models originally presented in paper into computer code and then report your insights, analysis and results. The learning activities and the available resources are designed to help you acquire or strengthen your skills as a financial professional, practitioner and junior researcher.

To achieve these objectives, you will take a series of tasks during the semester, which can be summarized by reading, working hard and contact me in case you need assistance. Consider the pseudocode below. It might not run in R, but it is still good to illustrate the learning process based on personal persistence and determination that I recommend you to follow. The learning process is much more complicated than this simplified pseudocode. However, complicated concepts can be represented in a simple form to better understand and communicate it.

```{r eval = FALSE}
# Initial condition.
learn <- FALSE
# Initial inputs assigned to study the topic.
inputs <- c(read, time, effort, assistance, others)
# Learning process.
while (learn == FALSE) {
  understand <- study(inputs) # Evaluate study function.
  if (understand == FALSE) {
    print("Add more inputs and try again.")
    inputs <- inputs + 1
    }
  else { # Understanding is the way to learn.
    learn == TRUE
    print ("Well done!")
  }
  }
```


## Mechanics.

The whole course is based on the following assumption: *you are expected to happily and enthusiastically work throughout the semester to accomplish my expectations as professor, complete the learning activities well on time, understand the subject and its applications as good as possible*. You are expected to follow the course calendar (at the end of this syllabus) as a main tool to prepare yourself in advance for every lecture topic, readings, and be aware of every future activity, assignment submission and exams. Following the course calendar is an easy way for us to be on the same page during the semester as we know with certainty the course progresses from day 1 until the final exam day. Most of the time, you will have to assign more than one week to complete a task in the calendar, this is why you are expected to manage your time efficiently so you can accomplish your course duties.

In this course, you are expected to consciously study the required material in advance as well as practice on your own because this will allow you to develop the necessary conditions to contribute with valuable comments and/or interesting questions in class. If you openly decide not to do this, then you might feel that you are getting behind, or perhaps you might not get advantage of the number of things that you can potentially learn in this course. In fact, if you fail to consciously read the required material in advance, the risk of getting frustrated increases, and frustration is the best way to lose interest, get lower marks and eventually fail in the worst case scenario. Then, if you are interested in reducing the risk of failing the course, I recommend you to consciously study the required material in advance as well as practice on your own as much as you want or need.

In this video, students from The University of Melbourne share great tips and strategies about how they get the most out of university lectures.

```{r echo=FALSE}
embed_url("https://youtu.be/Aa01-lwYllU")
```

For your convenience, and in accordance with some of [The Sustainable Development Goals](https://sdgs.un.org/goals) by the United Nations, see @UN17, all the compulsory readings and activities submissions are available in electronic format. Other complementary material and activities could be incorporated or altered during the semester depending on relevant news or events that do not exist at the moment, or that are hard to anticipate at the beginning of the semester. If that is the case, I will let you know in advance. As a student, you should be confident that all the course material and activities are perfectly suitable for an undergraduate student enrolled in a prestigious world-class university. In other words, there will not be an intellectual challenge that you cannot overcome with an appropriate amount of enthusiasm, time, work, determination, and assistance (if necessary). This course is designed in such a way that you can pass and learn as long as you invest the right amount of time and work.

I assume you are aware of the academic regulations dictated by the university. If you are not familiar with these, please review the corresponding student regulations. In this course, we will attach to them.

## Academic integrity.

We pledge to hold ourselves and our peers to the highest standards of honesty and integrity. Academic integrity violations including plagiarism and cheating are prohibited and may result in the failure of the assignment, failure of the course, and/or additional disciplinary actions depending on current regulations. We understand plagiarism as the presentation of another person's thoughts or words as if they were the student's own. For example, copying from textbooks and other sources (including the Internet) without due acknowledgment that the passages quoted are copied and without giving the source of those passages. 

Please watch the following video about plagiarism taken from York St. John University (UK) about understanding plagiarism.


```{r echo=FALSE}
embed_url("http://youtu.be/ptHIA5bMnio")
```


I strongly advise you not to construct a piece of work by cutting and pasting, or copying material written by other people into something you are submitting as your own work. No matter what pressure you may be under to complete an assignment, you should never succumb to the temptation to take a *short cut* and use someone else's material inappropriately. 

See the following video to illustrate this point:

```{r echo=FALSE}
embed_url("https://youtu.be/cUVAbvXjTeg")
```

Ethical behavior is implicit in the course mechanics and rules, and it will be explicit in several topics throughout the course material. Following the indications of this syllabus is a simple way and a clear example regarding how we can effectively pursue ethical behavior. Ethics concerns are inherent in business, economics and finance activities because the professionals in these fields frequently manage resources to achieve a range of objectives, not exclusively maximize profits. Pursuing ethical behavior also helps us to build solid institutions, which is consistent with the United Nations 17 sustainable development goals @UN17. Managing own or third-party resources entails a high degree of responsibility because people often face the alternative to apply unethical strategies to achieve their own interests. A proper discussion of the ethical aspect in the decision-taking process including conflict of interests is necessary to increase the awareness of young professionals like you. In the end, following an ethical code as a business practice can contribute to strengthening or building your own reputation -- one of the most significant assets you have, or are currently building.

Take a look at this video about integrity.

```{r echo=FALSE}
embed_url("https://youtu.be/m1AxHZSX5VA")
```

## Sustainable finance. `r fontawesome::fa("envira")`

I am certified as *carbon literate* by the UN Climate Change Conference and Coventry University. The certification represents a robust understanding of the climate context and a commitment to recognise ways to adjust our behaviour to reduce our carbon footprint, as well as influencing our social and professional circles. My view is that one way of achieving a positive impact over the environment and the society is to learn more about sustainable finance. 

According to the European Commission, sustainable finance refers to the process of taking environmental, social and governance (ESG) considerations into account when making investment decisions in the financial sector, leading to more long-term investments in sustainable economic activities and projects. Environmental considerations might include climate change mitigation and adaptation, as well as the environment more broadly, for instance the preservation of biodiversity, pollution prevention and the circular economy. Social considerations could refer to issues of inequality, inclusiveness, labour relations, investment in human capital and communities, as well as human rights issues. The governance of public and private institutions – including management structures, employee relations and executive remuneration – plays a fundamental role in ensuring the inclusion of social and environmental considerations in the decision-making process.

In this course, you will be exposed to an introduction about sustainable finance, climate change and green economy. In particular, you will acquaint yourself with the basic skills and tools for applying the sustainable finance mechanisms to a real-world policy or business context.

Learning materials are taken from The One UN Climate Change Learning Partnership [UN CC:Learn](https://unccelearn.org/), which is a joint initiative of more than 30 multilateral organizations helping countries to achieve climate change action both through general climate literacy and applied skills development. UN CC:Learn provides strategic advice and quality learning resources to help people, governments and businesses to understand, adapt, and build resilience to climate change.

Earth’s global average surface temperature in 2021 tied with 2018 as the sixth warmest year on record, according to an analysis by NASA:

```{r echo=FALSE}
embed_url("https://youtu.be/haBG2IIbwbA")
```
