---
title: ''
  html_document:
    df_print: paged
---

\newpage

# `r fontawesome::fa("tasks")` Learning resources and activities.

This course is conducted in Spanish and English. Most learning resources are in English, exams and homework assignments submitted in English. However, discussion forums, emails, and class sessions are conducted in Spanish. 

The learning activities are classified as graded, non-graded and extra marks. All graded activities represent 100% of your final grade; non-graded activities are relevant for your learning but are not graded, so if you fail to do them you will not get any mark deduction. Extra marks are applied as a bonus to your graded activities or final grade. 

The learning activities are also classified as individual and group activities. 

## Learning resources. `r fontawesome::fa("brain")`

Here is the list and description of available resources for you to learn the subject. My advice is to use as many resources as possible because they will allow you to learn the subject and develop the required professional competences that you need to have.

**Professor.** I have vast experience as an academic and researcher. I also have numerous postgraduate studies and willingness to help you in case you need assistance to better understand the course topics. You only have to contact me and follow my advice. 

Please see the video about professors:

```{r echo=FALSE}
embed_url("https://youtu.be/IzG85NDDo1Q")
```

**Class sessions.** We explain and discuss specific topics, ask and answer questions, review your study progress, and sometimes we conduct brief activities. Please note that the time available in class sessions is limited and we are not going to cover every single topic in full detail. Instead, we will use other resources and learning activities to cover the rest of the topics. You are expected to attend on time, participate, and engage in our discussions. I expect you to use your computer because you may need to use R, see the PDF textbook, or your own homework during the session.

In case of virtual learning, it is OK if you want to keep your microphone on, and camera on or off as most of the time we are going to share the screen during the class. For your convenience, unless otherwise stated, class Zoom sessions are recorded and available for you. Internet service may fail during class sessions, but this is a risk we all face. 

See the following video for a good recommendation from Prof. Fleisch valid for online sessions and traditional course sessions:

```{r echo=FALSE}
embed_url("https://youtu.be/KX-sg1HXAws")
```

<!-- **Audio files (if available).** I explain part of the course material with my *sweet melodic* voice. Some students might have difficulties at understanding the required readings and I believe these mp3 audio files are useful to better understand some topics. It is compulsory to listen to them before the class session. Please note that not all the course material is discussed in audio files, for this reason you are not supposed to listen to audio files and ignore the rest of the course material, all resources complement each other. Audio files are not listed in the course calendar, but it will be easy for you to identify which audio file corresponds to each course topic. -->

**Discussion forums.** There are discussion forums in which we can interact. The interesting thing about discussion forums is that we can all read how the discussion is progressing and we can all participate. The logical evolution of ideas remains recorded while you receive my feedback and comments. Given that we have limited time in class sessions, we occasionally need discussion forums. We may also use the discussion forums as a way to submit individual activities. 

**Email.** You are free to contact me by email at any time: <tt>`<martin.lozano@udem.edu>`</tt>. I also send group emails with important information, so please make sure my email address is not in your spam list. If I ever take longer than expected to answer an email or any other request, please insist and kindly remind me.

**Meetings.** Regardless of face-to-face or virtual learning, we can arrange 30 minute Zoom online meetings if you need further assistance or any other issue you want to discuss with me. Meetings can be individual or in group. You only have to ask for it by email to check for my time availability. If you need more time we can arrange more meetings or more time, whatever is best. This is the Zoom meeting link https://us02web.zoom.us/j/9209945512

**Book.** The book (or books) is one of the main pillars of this course. In my experience you mainly learn by reading and then reinforce by doing, although you have other diverse activities in this course. The book authors are one of the best in their field: John C. Hull (University of Toronto) @Hull9, Richard A. Brealey (London Business School), Stewart C. Myers (Sloan School of Management Massachusetts Institute of Technology) and Franklin Allen (Imperial College London) @brealey2020principles in the case of ARF and IF; Rob J. Hyndman and George Athanasopoulos (Monash University) @49018680cf534023b6ae0f4e933c475d in the case of EMF. These books are not only good for intermediate and advanced undergraduate degrees but also for first year master degree. I prefer to use original book versions rather than translations because according to my experience these are not always as good as the original English version, and in some cases are not available.

**Tutorial.** I have written a specialized online tutorial to explain how to implement some topics and estimate models using data. The tutorial can help you to understand how to go from the paper (textbook chapters) to R code. This is sometimes known as literate programming. My tutorials include @lozanoARF, @lozanoEMF, and @lozanoIF among others.

**Others**. All learning resources described above represent a good resource for your own study of the course material. There are plenty of Internet resources that you will have to use, from databases, [YouTube](https://www.youtube.com/) videos, [GitHub](https://github.com/) public repositories, specialized programming blogs, books, electronic books, etc. See the resource list at the end of this document for further details. You are encouraged to read articles, reports and news on your own to enhance and expand your understanding about how theoretical concepts relate with current real-life events. [The Economist](https://www.economist.com/), [The Financial Times](https://www.ft.com/), [The Guardian](https://www.theguardian.com/), [The Wall Street Journal](https://www.wsj.com/), [MarketWatch](https://www.marketwatch.com/), [Reuters](https://www.reuters.com/), [Bloomberg](https://www.bloomberg.com/), [Bureau of Economic Analysis](https://www.bea.gov/), [Banxico](https://www.banxico.org.mx/), [Project Syndicate](https://www.project-syndicate.org/), [The New York Times](https://www.nytimes.com/), [El Financiero](https://www.elfinanciero.com.mx/) (México), [El Confidencial](https://www.elconfidencial.com/) (Spain), [OECD](https://www.oecd.org/), are a good way to grasp contemporary insights related with this course. Other references to support your learning process include economic and financial reports from private banks such as Banamex and BBVA, and think tanks websites such as [The Mexico Institute](https://www.wilsoncenter.org/program/mexico-institute), [México cómo vamos](https://mexicocomovamos.mx/), [CIDAC](http://cidac.org/), [IMCO](https://imco.org.mx/), [COMEXI](https://www.consejomexicano.org/), among many others. My advice in this respect is rather simple: *the more you read the more you learn*.

## Graded activities. Exams: $E_1$, $E_2$ and $E_F$. `r fontawesome::fa("grimace")`

We have 2 partial exams $E_1$, $E_2$ (40% of the final grade), and one final exam $E_F$ (30% of the final grade) in English. Every topic discussed in this course is subject to be evaluated in exams. Therefore, if you are looking forward to achieving an outstanding final grade in this course, my sincere advice is to take class notes during the semester. 

Please take a look at this video about taking notes:

```{r echo=FALSE}
embed_url("https://youtu.be/pAvPE0lPlqE")
```

This one is good as well. In this video, students from The University of Melbourne talk about using digital tools to take notes and stay focused.

```{r echo=FALSE}
embed_url("https://youtu.be/Lll3MsS5chk")
```

**When?** Exams will be taken according to the course calendar, these dates correspond to the official dates dictated by the university partial and final exam calendars. Both $E_1$ and $E_2$ are 1.5 hours activities during the class session, and the $E_F$ lasts 2 hours. In the case of 3 hour class sessions, the exam takes place in the first part of the class, and we review the exam answers the same day in the second part of the class session. In the case of graduated students we may need to change the final exam date for administrative reasons. 

Please consider the following recommendations about exams:

```{r echo=FALSE}
embed_url("https://youtu.be/w1w0dkHdakE")
```

**Where?** You do not have to be physically in the classroom to take the exams, you can take the exams anywhere you want as the exam is fully taken, answered and delivered in electronic format. You only have to make sure you have a good Internet connection. I will be available during the exams in Zoom, you do not have to log in the Zoom session, you only have to know I will be available in case you need it. In the case of 3 hour class sessions, you will have to log in to the Zoom session in the second part of the class to answer the $E_1$ and $E_2$ exam together.

**How many questions?** In the case of $E_1$ and $E_2$, I include 4 questions and you have to answer 3 so you have the chance to select the 3 questions that you know the best. In the case of $E_F$, I include 5 questions and you have to answer 4. All questions have the same weight. It is not an option to answer all the exam questions, if you do that you may earn a significant mark deduction. The $E_F$ covers all the course topics/activities. For your convenience, I take one question from $E_1$ and one question from $E_2$, and I include them with a minor change in the $E_F$. This means that if you study $E_1$ and $E_2$ very well, you should be able to answer at least 50% of the $E_F$ correctly. In case you take the exam on a different date for any reason, your $E_1$ or $E_2$ will have 3, not 4 questions as stated above. This means that you will not have the benefit of not answering one exam question. The same principle applies for the $E_F$.

**What are typical exam questions?** I always let my students keep their own partial exams, so I guess you can find old partial exams. The course material evolves and exam questions change every semester. However, looking at old exams can give you a good idea about what kind of questions to expect in the exam. I always include some questions that require the use of R. Exam questions usually require some analysis and interpretation of results. For your convenience, we have review class sessions and/or mock exams before each graded exam. If we need more time to review we can use the discussion forum. 

See some recommendations about review sessions:

```{r echo=FALSE}
embed_url("https://youtu.be/XoHx_UIgtt0")
```

**Individual or in groups?** All exams $E_1$, $E_2$ and $E_F$ are group activities: no more than 4 students per group, otherwise you will earn a significant mark deduction. Groups are defined by yourself and will remain fixed throughout the semester. I will allocate a name to each group which corresponds to the name of a Jupiter moon. These groups are the same for the homework assignments $H$. The class list could change during the semester as some students may enroll later or drop the course, in this case groups members may change, but the maximum number of students per group remains the same. Your group will have private access to a Deepnote project, this project is private as only your group and I will be able to edit the contents. 

**What are the mechanics?** The exam instructions will be available for you according to the course calendar in an electronic format as an *.ipynb* file. The instructions will automatically appear in Blackboard 5 minutes before the class session starts. As soon as the file is available in Blackboard, you will have to download it and upload it in your own Deepnote project named as your group (the name of a Jupiter moon), and solve it online with your group. By the deadline, I will make a copy of your notebook to review it and mark it. There is no need to submit your exam file as I have access to your Deepnote project to make an electronic copy, you only have to make sure to finish before the deadline. A few days later, you will receive your group mark and some comments or feedback in the Deepnote read-only project. During the exam, I may visit your notebook quietly to see `r fontawesome::fa("eye")` your progress.

**Do all group members receive the same mark?** Not necessarily. Individual activities may represent extra marks. Also, if one member does not contribute then he or she will receive a zero mark. I assign a group mark which is the same for all the group members. However, you have to complete an auto and co-evaluation. Your individual exam mark is then a combination of a group mark assigned by me, and the auto and co-evaluation, assigned by you and your colleagues. Full details below.

**Can we open the textbook during the exam?** Yes, you are free to use the Internet and all course material if you need it, including the textbook and tutorial. Exams are designed to evaluate your reasoning, coding and analytical skills rather than your capability to memorize concepts and do an Internet search. Exams are designed in such a way that you will not find the answers online, in a textbook or a test bank. Although the questions are designed according to the course material, these questions are most of the time new and original. The only constraint is that you are expected to answer the exam on your own with the help of your own group, no more than 4 students per group. 

**Are we going to review the exam answers?** Yes, the class session after the exam is a Zoom session to solve the exam questions and the correct approach to answer the questions. This applies only for $E_1$ and $E_2$, we cannot do it for $E_F$ because classes are over by then. Exam questions are open and there are usually more than one way to answer them correctly, so we will discuss a range of correct answers and common mistakes. Sometimes students are used to closed and unique answers, but this is frequently not the case in this course. If we need more time to discuss the exam answers, we can use the discussion forum, Deepnote, or you can ask for an online meeting. This is important as we usually have a limited time during the class session. Correcting your own mistakes in the exam is a good way to learn and practice towards the final exam.

**What if we fail to understand our own mistakes?** Regardless of the activity, you are expected to contact me in case you fail to fully understand your mistakes. I may ask you to answer them again before we can discuss your own mistakes in a meeting. Please note that the grade you get in the exam, including individual extra marks and the auto and co-evaluation is your registered partial grade.

## Graded activities. Homework assignments: $H_1$, $H_2$ and $H_3$. `r fontawesome::fa("grimace")`

We have 3 homework assignments $H_1$ and $H_2$ (30% of the final grade), and non-graded homework $H_3$ in English. Assignments are good practice towards exams. Therefore, if you are looking forward to achieving an outstanding final grade in this course, my sincere advice is to start working on them as soon as possible. You can always show me your assignment progress and I can give you comments to improve. Deepnote allow you to add comments to some specific part of your assignment, if you tag me as <tt>`@martin.lozano@udem.edu`</tt> then I will receive an email notification to review your specific question, then I will answer you back as a reply to your original comment and you will receive an email notification as well.

**When?** The fixed deadline to complete homework assignments is 10:00 a.m. on the day marked in the course calendar and there is no late homework policy at all. This basically means that if you fail to do the assignment, and/or if you have an empty, wrong, or corrupted Deepnote notebook by the deadline, then the group mark is zero. This is important because sadly there are always some students who forget or simply ignore this information no matter how much I insist on this. The $H_1$ is due a few days before $E_1$; $H_2$ is due a few days before $E_2$; and $H_3$ is due a few days before $E_F$. I recommend taking enough time to plan and execute the required tasks in the assignments. Usually, low marks in this activity are not precisely because the assignment is difficult, but because the group started the assignment a couple of days before the deadline.

**What are typical assignment questions?** You should expect applied questions, some of them with a research-oriented approach. These questions will require you to develop computational code in R. You will need to learn new things and conduct some research to be able to tackle them correctly. However, you are not alone in this process, you have a long list of resources described in this syllabus including my help in the form of synchronous Zoom meetings, or asynchronous communications via Deepnote comments, or email communication.

**Individual or in groups?** This is a group activity. These groups are the same for the exams. Please see the exam section above to review the definition of the groups and relevant policies. 

**What are the mechanics?** This is similar to the case of exams. The assignment instructions will be available for you in an electronic format in the read-only Deepnote project. As soon as the file is available, you will have to upload the instructions in your own Deepnote project named as your group (the name of a Jupiter moon), and solve it online with your group. By the deadline, I will make a copy of your notebook to review it and mark it. There is no need to submit your assignment file as I have access to your Deepnote project to make an electronic copy, you only have to make sure to finish before the deadline. A few days later, you will receive your group mark and some comments or feedback in the Deepnote read-only project.

**Do all group members receive the same mark?** The same as in the case of exams.

**Are we going to review the homework assignment answers?** The same as in the case of exams.

**What if we fail to understand our own mistakes?** The same as in the case of exams.

**Why is $H_3$ a non-graded activity?** The $H_3$ is a special assignment that is designed to help you to practice and study for your final exam by learning from your previous mistakes. It has a deadline but it is a non-graded activity. Given that it is non-graded, this activity is optional. The $H_3$ instructions are the following: You are required to (1) correct all your mistakes in all your previous graded activities, including all the four $E_1$ and $E_2$ questions, and assignments; and (2) complete all your missed extra mark activities, mostly from DataCamp. The format and delivery is the same as the rest of the assignments. You can do it in group or individually. You will not receive $H_3$ as by then you will have access to all exam and assignment answers. In any case, you can ask me to review it if necessary. 

## Extra marks activities. `r fontawesome::fa("grin-hearts")`

As with any extra mark activity, you do not lose marks if you fail to complete them, but you can get extra marks over your graded activities if you complete them on time. In case you are taking two courses with me this semester, then the extra marks that you get in one course will be valid for the second and vice versa.

For every DataCamp course and skill track listed in the course calendar and completed on time you get a nice PDF certificate that looks good in your CV and LinkedIn profile. It also can help you to have more tools to write your homework assignments, exams, write your own PEF, and apply for interesting jobs. The list of courses, skill tracks and projects that apply for this course is available in the course calendar. 

I find the DataCamp a very good alternative, although not the only one, to learn R and data science. Normally, people have to pay for a DataCamp account to learn data science, and some firms have to pay for this kind of training to help their employees to learn R or Python. Current fees for a DataCamp premium individual account is about 33.25 USD per month, about 200 USD for the semester. However, as my student, you have free individual access for full access to all DataCamp courses and resources for the whole semester as long as this firm keeps its promise to make this access free for my students. In exchange, DataCamp ask for a mention on social media, please find all the resources and instructions on these [communication guidelines.](https://docs.google.com/document/d/1Dv-L036CZWsZCmn9W5p0ikgetlc4GcT-NQ9Rp_HebE0/edit) Are you able to provide this?

<!-- [^6]: Please note that DataCamp is not the only alternative to learn R. There are other free alternatives available in the web such as [Swirl.](https://swirlstats.com/) You can find many free electronic resources to learn R in the reference section at the end of this syllabus. There are also some students who find the tutorials (developed by myself) a good enough resource to learn R. However, there are other students who need more specialized courses, or more basic courses to understand the logic of programming in R and some other extensions. In my attempt to offer you as many free and useful resources as possible, you have a DataCamp account. According to Martijn Theuwissen Co-founder and COO at DataCamp, they are no.1 ranked Forbes certifications. -->

I understand learning R could represent a source of uncertainty and stress for some of my students. This is why I have developed and gathered a vast amount of varied and free resources to learn R in the reference section of this syllabus. In fact, you have more free resources that you need in the semester. It is true that you will have to learn a few things on your own, and it is true you will have to investigate to learn some other things. You are expected to learn how to learn as well and as quickly as you can because in the job market you need to constantly learn and apply new knowledge, and solve problems that currently do not exist. A competitive graduate is not the one who learns what was taught in class, a competitive graduate is the one who also manages to learn how to learn.

**DataCamp (courses, skill tracks, and projects).** Starting from the second activity completed on time, you will earn extra marks over your next exam, it could be $E_1$, $E_2$ or $E_F$. These activities will be available for you to complete in your DataCamp Assignments section, and listed in the course calendar as *extra marks* tag. Projects and courses can be completed in a few hours, but skill tracks require more time as they include more than one regular course. The amount of extra marks is a function of the cumulative number of activities during the semester. In particular, you earn $n-1$ extra marks per activity $n$. 

For example, if you complete 9 activities in the semester, you earn a total of:

$\displaystyle \sum_{n=1}^{9} (n-1) = 36$. 

According to this example, extra marks will be assigned as 0, 1, 2, 3, 4, 5, 6, 7, and 8. See the course calendar for the correspondent deadlines of DataCamp activities.

**DataCamp assessments.** DataCamp assessments are individual activities that allow you to get extra marks over your final grade $F$. Yes, over your final grade. These are time-limit online evaluations of your knowledge of R. DataCamp marks your assessment as N (novice), I (intermediate), and A (advanced) depending on your own performance. The rule to allocate the extra marks over your final grade $F$ is the following: 0 for N; +1 for I; and +2 for A. Assessments will be available in your DataCamp Assignments section and in the course calendar as *super extra marks* tag. Assessments are completed during the class session and although DataCamp allows you to complete the assessment twice, I will take your first try as your grade.

Some students may have a DataCamp activity completed. If your certificate is older than the starting date of this current academic term, then you will have to do it again. In case DataCamp do now allow you to do it again, then you can substitute it by one of the following DataCamp Career Tracks: (1) R programmer; (2) Data Scientist with R; (3) Data Analyst with R; (4) Quantitative Analyst with R; (5) Statistician with R; or (6) Machine Learning Scientist with R. If this is the case, please let me know and share your certificate with me by email before the deadline so I can assign the corresponding extra marks.

**Stickers.** There are some opportunities throughout the semester to get extra marks. In this course, extra marks are allocated in the form of stickers, every sticker stands for 5 extra marks on your next exam $E_1$, $E_2$, or $E_F$. They are called *stickers* because I give real stickers to my students. Stickers are assigned by merit. It is not very easy to get a sticker, but it is worth a try. The record so far is one student who got 30 extra marks over the $E_F$, and he finally passed the course partially because of that.

**The wheel of fortune.** I roll a virtual wheel of fortune three times in the semester to randomly allocate extra marks to a lucky group of students. These extra marks are allocated to the next exam $E_1$, $E_2$, or $E_F$. Make sure to attend this class as this is one requirement to get the extra marks if you are selected by the wheel of fortune.

**Mock exams.** We have three mock exams $ME_1$, $ME_2$ and $ME_F$. These are similar to regular exams, taken during class before the real and graded $E_1$, $E_2$ and $E_F$ exams. They represent an opportunity to get familiar with the examination process, logistics and level of difficulty of the real and graded exams. Mock exams are group activities, usually one question. Only if your group answers the question 100% correctly then your group will receive a sticker. I will post the correct answer after the deadline. 

**Mentimeter.** We may have a few sessions in which we include a mentimeter activity. This activity is subject to be evaluated and if it is, then the top 10 best answers will have extra marks.

## Non-graded activities. `r fontawesome::fa("meh-rolling-eyes")`

**DataCamp webinars.** You are free to attend live webinars organized by DataCamp. See the *live events* DataCamp section for the upcoming webinars in this semester. Please note that you have to register to attend. Let me know which ones you are planning to attend. 

**Videos.** You can record and submit one video per period (up to one per partial exam). This is an individual non-graded activity, in Spanish. The submission of this activity is by the discussion forum. I recommend you to upload the video as a YouTube link or any other similar platform so you can submit only the web url in the discussion forum. I would like to avoid others downloading the video, so I believe sharing the link is the best way to submit it. By sharing the video url will allow you to delete your video after the semester ends if you wish. The design of the video and the length is free although you have to start by introducing yourself and the course name. 

There are four types of videos.

* **Type 1: Feynman.** The Feynman technique for teaching and communication is a mental model (a breakdown of a personal thought process) to convey information using concise thoughts and simple language. The Feynman model is named after the Nobel prize-winning physicist Richard Feynman, who was recognized as someone who could clearly explain complex topics in a way that everybody --- even those without degrees in the sciences --- could understand. He was also named *The Smartest Man in the World* in 1979. According to him: *The person who says he knows what he thinks but cannot express it usually does not know what he thinks.* There are four simple steps to the Feynman technique: (1) choose a concept; (2) teach it to a toddler; (3) identify gaps and go back to the source material; (4) review and simplify. Teaching it to a toddler should not take it literally, it basically means that your explanation should be as clear and simple as a toddler could understand it. 

Further details about the Feynman technique here:

```{r echo=FALSE}
embed_url("https://youtu.be/_f-qkGJBPts")
```

* **Type 2: The interview.** You can interview someone who can share some thoughts with us. For example, you can interview your mom or dad to discuss topics about his or her job. You are free to design the questions and the format. This could be a good opportunity to know how people in a specific industry tackle business problems, or challenges of people working in the public sector.

* **Type 3: Your pet.** You can show us your pet. Tell us something about your pet, and how special it is for you and your family. Do you have a spider `r fontawesome::fa("spider")`, fish `r fontawesome::fa("fish")`, frog `r fontawesome::fa("frog")`, cat `r fontawesome::fa("cat")`, dog `r fontawesome::fa("dog")`, craw `r fontawesome::fa("crow")`, dragon `r fontawesome::fa("dragon")`? All kinds of pets are welcome.

* **Type 4: Your hobby or talent.** You may have a special artistic or sport talent you would like to share with us or a hobby which could be interesting for all. This could be a good opportunity to get to know you better.

<!-- **Discussion forums.** -->

<!-- Discussion forums are a good opportunity to discuss topics further while keeping track of ideas, procedures, results and conclusions. The use of discussion forums represent an extension of the class session and learning activities. My advice is to read the course material to be prepared for the discussion forum questions. My view is that discussion forums are not a repository of individual answers but an opportunity to conduct a proper discussion. Then, please make sure that every time you post a contribution you read the current state of the discussion so you can add value to it. We also use the discussion forums as an open space to ask me questions about the course contents. Please subscribe to the discussion forum so you can receive email notifications. This is convenient because I normally do not announce new discussions. There is no fixed frequency for this activity, most of the time it depends on the students interests. You should add your picture in the settings so we can easily match face with name. This is an individual non-graded activity, in Spanish. -->



